---
title: "p8105_hw5_bsr2136"
author: "Barik Rajpal"
date: "11/9/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 0

```{r p0, warning=FALSE}
dir.create("files_for_hw5")
```

## Problem 1

```{r p1}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

### Function to remove missing values

```{r p1.1}
remove_missing <- function(x) {
  
  if (is.numeric(x)) {
      for (i in 1:length(x)) {
          if (is.na(x[i])) {
              x[i] = mean(x,na.rm=T)
          }
      }
  }
  else if (is.character(x)) {
          for (i in 1:length(x)) {
              if (is.na(x[i])) {
                  x[i] = "virginica"
              }
          }
  }
  else stop("Not numeric or character")
  x
}
```

### Applying the function to iris_with_missing df

```{r p1.2}
map(iris_with_missing,remove_missing)
```

## Problem 2

```{r p2, message = F}
names_df <- tibble(
                short_file = list.files("./files_for_hw5"),
                filenames = list.files("./files_for_hw5") %>%
                str_c("./files_for_hw5/",.)
            )

names_df <- names_df %>%
  mutate(list = map(pull(names_df,filenames), read_csv)) %>%
  unnest(list) %>%
  mutate(arm = ifelse(str_detect(short_file,"con"),"Control","Experimental"),
         subject_id = as.numeric(str_match(short_file,"[0-9]+"))
         ) %>%
  select(arm,subject_id,everything(),-short_file,-filenames) %>%
  pivot_longer(cols = week_1:week_8,
              names_to = "week",
              values_to = "observations") %>%
  mutate(week = as.numeric(str_match(week,"[0-9]+"))
           )

names_df %>%
  ggplot(aes(x=week,y=observations,color=as.factor(subject_id))) + 
  geom_line() +
  facet_grid(.~arm) + labs(color = "subject_id")

```

The experimental subject observation values increase fairly significantly over time. The control subject observation values fluctuate over time, but don't noticeably increase or decrease over time.

## Problem 3

### sim_regression function

```{r p3.1}
sim_regression = function(n = 30, beta0 = 2, beta1 = 0, sigma_2 = 50) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, sigma_2)
  )
  
  ## NEED TO EDIT THIS PART TO CHANGE FOR HOMEWORK
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
  
  ## END OF WHAT NEEDS TO BE EDITED
}
```

### running sim_regression 10,000 times for beta_1 = {0,1,2,3,4,5,6}

```{r p3.2}
sim_results_0 <- rerun(10000, sim_regression(beta_1 = 0)) %>% 
  bind_rows()

sim_results_1 <- rerun(10000, sim_regression(beta_1 = 1)) %>% 
  bind_rows()

sim_results_2 <- rerun(10000, sim_regression(beta_1 = 2)) %>% 
  bind_rows()

sim_results_3 <- rerun(10000, sim_regression(beta_1 = 3)) %>% 
  bind_rows()

sim_results_4 <- rerun(10000, sim_regression(beta_1 = 4)) %>% 
  bind_rows()

sim_results_5 <- rerun(10000, sim_regression(beta_1 = 5)) %>% 
  bind_rows()

sim_results_6 <- rerun(10000, sim_regression(beta_1 = 6)) %>% 
  bind_rows()
```

